### 2015-03-04 paper_40_cri.tex
update sensitivity description

                    Project ID & String  & Required \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Requirements Scheduled & Integer & Required \\
                    \myrowcolour%
                    Actual Requirements Released & Integer  & Required \\

@@

    \subsection{SENSITIVITY OF CRI}
    \label{sub:sensitivity}

        Some simulations will be run with data from each given distribution.  Then the CRI scores
        will be analyzed.
        For more on sensitivity analysis in statistical modeling, see \cite{Saltelli2000}.

>>>>

                    Project ID & String  & Required \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Scheduled Requirements & Integer & Required \\
                    \myrowcolour%
                    Actual Requirements & Integer  & Required \\

@@

    \subsection{SENSITIVITY OF CRI}
    \label{sub:sensitivity}
        The sensitivity of the formulas should be tested as the scores should not
        flucate drastically for similar values.  There are 2 possible techniques
        for testing the sensitivity of the formulas. 
        \begin{description}
            \item[First] Given the historical data that has been collected,
                alter the values by some small random amount.  Then recalculate
                the CRI element score and compare with the original score.  This
                technique can be repeated many times in order to verify
                small changes do not largely affect the score.  Thus, a 
                formula which is not overly sensitive. 
            \item[Second] Another technique is to use Monte Carlo methods to 
                randomly generate input values for the element functions.  
                This can be done by finding the distributions of the historical
                data, and randomly selecting from that distribution.  If historical
                data is not available, then For more on sensitivity analysis 
                in statistical modeling, see \cite{Saltelli2000}.
        \end{description}

        .
